%\documentclass[letterpaper,12pt]{book}
%\usepackage[spanish]{babel}
%\usepackage{graphicx, color}
%\usepackage{amsmath}
%\usepackage{amscd}
%\usepackage{youngtab}
%\usepackage{titlesec}
%\usepackage[latin1]{inputenc}
%\usepackage{listings}
%\usepackage{multicol}
%\usepackage{enumerate}
%\usepackage{amssymb}
%\usepackage{amsthm}
%\usepackage{syntonly}
%\usepackage{fancyhdr}
%\begin{document}
\begin{thebibliography}{99}

\bibitem{5} Julius Wess and Bagger, {\it Supersymmetric and Supergravity}

\bibitem{4} Steven Weinberg, {\it The Quantum Theory of Fields}, Vol.III
(Supersymmetry), Cambridge University Press, 2000.

\bibitem{7} P. Ramond, Phys. Rev. D3, 2415 (1971). Superstrings -
\emph{The first 15 years of Superstrings Theory}, J.H. Schwarz,ed.
(World Scientific, Singapore, 1985).

\bibitem{2} Ian J. R. Aitchison, {\it Supersymmetry and the MSSM: An Elementary
Introduction}, Oxford University Departament of Physics, 2004, 2005.

\bibitem{6} D. Bailin and Love, {\it Supersymmetric Gauge Field
Theory and String Theory}, Institute of Physics Publishing, Bristol
and Philadelphia, 1994.

\bibitem{Sohnius} Martin F. SOHNIUS, {\it INTRODUCING SUPERSYMMETRY},
\emph{Phys. Rept.}, (Review Section of Physics Letters)128, Nos, 2
\& 3 (1985)39-204 North-.Holland, Amsterdam.

\bibitem{1} Stephen P. Martin, {\it A SUPESIYMMETRY PRIMER}, Randall Physics Laboratory,
University of Michigan Ann Arbor MI 48109-1120 USA, 1999.

\bibitem{3} Diego R. Q. Alejandro, {\it Phenomenology of Bilinear Broken R-parity},
Universidad de Valencia, Departamento de Física teórica, España.

\bibitem{Neutrino Masses and Mixings} M. Hirsch, M. A. Díaz, W. Porod, J. C.
Rom$\tilde{a}$o and J. W. Valle, {\it Neutrino Masses and Mixings
from Supersymmetry with Bilinear R-Parity Violation: A Theory for
Solar and Atmospheric Neutrino Oscillations},
[arXiv:hep-ph/0004115v2].

\bibitem{Haber y Kane} H. E. Haber and G. L. Kane, \emph{Phys. Rept.}
\textbf{117} (1985) 75.

\bibitem{Gunion y Haber} J. F. Gunion and H. E. Haber, \emph{Nucl. Phys.}
\textbf{B272}, (1986); \emph{Nucl. Phys.} \textbf{B278}, 449 (1986);
\emph{Nucl. Phys.} \textbf{B307}, 445 (1988). (E: \emph{Nucl. Phys.}
\textbf{B402}, 567 (1993)).

\bibitem{Hunter guide} J. F. Gunion, H. E. Haber, G. L. Kane and S.
Dawson, {\it The Higgs Hunter's Guide}, Perseus publishing,
Cambridge Massachusetts, 2000.

\bibitem{SUSY Higgs at the LHC}G. Bélanger, F. Boudjema, F. Donato, R. Godbole
and S. Rosier-Lees, {\it SUSY Higgs at the LHC: Effects of light
charginos and neutralinos}, [arXiv:hep-ph/0002039v1].

\bibitem{NOVEL SCALAR} F. de Campos, M. A. García-Jareño, Anjan S.
Joshipura, J. Rosiek and J. W. F. Valle, {\it NOVEL SCALAR BOSON
DECAYS IN SUSY WITH BROKEN R-PARITY}, [arXiv:hep-ph/9502237v2].

\bibitem{Acoples con tan de theta} M. Hirsch, M. A. Diaz, W. Porod, J. C. Romao
and J. W. F. Valle, \emph{Pys. Rev.} D \textbf{62} (2000) 113008
[hep-ph/0004115].

\bibitem{Pich} A. Pich,  {\it THE STANDARD MODEL OF ELECTROWEAK
INTERACTIONS}, Departamento de Física Teorica, IFIC, Universitat de
Valencia-CSIC, (2005) [arXiv:hep-ph/0502010V1].

\bibitem{Gordon Kane} Gordon Kane, {\it Modern Elementary Particle Physics},
Addison-Wesley Publishing Company, 1987.

\bibitem{Peskin} Michael E. Peskin and Daniel V. Schroeder, {\it An introduction
to Quantum Field Theory}, Addison-Wesley Publishing Company, 1995.

\bibitem{Griffiths} David Griffiths, {\it Introduction to Elementary particles Physics}, John
Wiley \& sons.inc, New York, 1987, Pag. 198.

\bibitem{Akeroyd} A. G. Akeroyd, M. A: Diaz and J. W. Valle, Phys. Lett. B \textbf{441} (1998)
224 [hep-ph/9806382].

\bibitem{Dias} M. A. Diaz, M. Hisch, W. Porod, J. C. Romao and J. W. Valle,
Phys, Rev. D \textbf{68} (2003) 013009 [arXiv:hep-ph/0302021].

\bibitem{SPheno} W. Porod,  {\it SPheno, a program for calculating
supersymmetry spectra, SUSY particle decays and SUSY particle
production a $e^{+}e^{-}$ colliders}, Institut fur Theoretische
Physik, Universitat Zurich, Switzerland, (2004)
[arXiv:hep-ph/0301101V4].

\bibitem{tortola} Michele Maltoni, ThomasSchwetz, Mariam Tortola, José W. F. Valle
{Status of global fits to neutrino oscillations}, (2007)
[arXiv:hep-ph/0405172v6].

\bibitem{signals in R-parity} D. Aristizabal, W. Porod, D. Restrepo, Carlos E. Yaguna,
{Novel Higgs decay signals in R-parity violating models}, PHYSICAL
REVIEW D \textbf{78}, 015015 (2008)

\end{thebibliography}

%\end{document}
